A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-14 writedown/zm/paper.water/main.tex
another round...

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \input{tcilatex}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Tuesday, November 11, 2014 22:18:30}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

@@

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}

\date{\today}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses gropu cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
}
[\recheck{please see the red part in Sec. III B. The order of the paragraphs are also rearranged.}]

@@

All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs,
pronk2013gromacs} complied by GNU C compiler with single-precision floating
point. The size of the systems and corresponding number of molecules used
for MD simulations are summarized in Tab.~\ref{tab:tmp1}. The benchmark
quantities were calculated in either canonical (NVT) or isothermal-isobaric
(NPT) ensemble, with equilibrium temperature $T=300$~K. In order to simulate
at the desired temperature, the systems $S_{1}$ and $S_{1}^{\prime }$ were
coupled to Nos\'{e}-Hoover~\cite{nose1984molecular,hoover1985canonical}
thermostat with time-scale $\tau _{T}=1.0$~ps, while systems $M_{1}$, $%
M_{1}^{\prime }$, $L_{0}$, $L_{1}$ and $L_{1}^{\prime }$ were coupled to
Langevin thermostat with time-scale $\tau _{T}=0.1$~ps. In the NPT
simulations, the systems were further coupled to the Parrinello-Rahman
barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs
implementation) with time-scale $\tau _{P}=0.5$~ps to equilibrate the system
at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
of 0.001~ps.

The neighbor lists were updated every 5 time-steps.
\recheck{The Gromacs by default uses the group cut-off scheme, while the ZM method suggests
  an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between
  these cut-off schemes is discussed in detail in e.g.~Ref.~\cite{hunenberger1998alternative,baumketner2009removing}.
  We adopted the atom based cut-off scheme in the simulations using the
  SPME (short-range part) and ZM electrostatic methods.
  In order to mimic the atom cut-off scheme in the Gromacs group cut-off implementation,
  the radius for neighbor list
  updating was set 0.3~nm larger than the cut-off radius (the maximum of
  Coulomb cut-off and the van der Waals cut-off). 
}

@@

The short-range part of SPME method was cut-offed at 1.9~nm,
and was smoothed in a shell of $0.05$~nm width by the
Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
reciprocal space grid spacing was set to 0.06~nm, with B-Spline
interpolation order of 6. These parameters were chosen to be more accurate
than the Gromacs default choices (grid spacing 0.12~nm and interpolation
order 4).
\recheck{The conducting boundary condition was used with SPME.}
The splitting parameter was optimized by the error estimate, which is implemented in Gromacs by tool \textquotedblleft 
\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
optimized real space and reciprocal space force computing errors were
equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
precision almost reaches the limit of the single-precision representation of
the floating point numbers.
% [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]

@@

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm cut-off radius and the
experimental dielectric constant $\varepsilon _{\text{rf}}=80$.

The van der Waals interaction was always cut-offed at 1.2~nm, and it was
modified in a shell of $0.05$~nm width near the cut-off sphere by the
Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
The final configuration of $L_{1}^{\prime }$ was used as initial
configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
which means the system is in desired thermodynamic state. [ {\color{blue}
COMMENT: If there are any specific conditions only for the pressure
calculation, please state around here or elsewhere.] [\recheck{No.}]}

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
little}. Although the splitting parameter, $\alpha $, also does not have
significant influence on almost all these thermodynamic quantities for $l=1$%
, only the isothermal compressibility admits a weak dependence. Overall, the ZM\
agrees with the SPME results without any bias and out-performs the RF.

{\color{red} It should be noticed that in the calculation of the chemical
potential, the energy correction plays an important role. In the case of $%
l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
final result. By increasing $l$ or $\alpha $, this contribution becomes more
significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
respectively. [\color{blue}COMMENT: We will clarify what is the "energy
correction" after making SecII, and describe the relation to IPSp after
making Appendix B.] }

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} }
\label{fig:pres-comp}
\end{figure}

@@

It should be noted that even with the system $L_{0}$ that
contains 13824 water molecules, the fluctuation
(measured by standard deviation) of the pressure is roughly 100~Bar, which
means that it is very difficult to achieve very accurate estimate for this
quantity. In practice a pressure error of 20~Bar is still acceptable.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
and not shown in your report. right? } \recheck{Right, it was not shown}]}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite{vanderSpoel2006origin},
therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any system-size dependency and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
the accuracy. Since a slow convergence is also known for the dielectric
constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
and confirm the sufficient convergence w.r.t.~the length of the
trajectories.

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
method is qualitatively wrong, and the accuracy of the ZM method is much
higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
highly consistent with the SPME result, and $l=2$ seems the best. In the
system of larger size ($L_{1}$), the accuracies of the ZM method is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.
\recheck{
  The Kirkwood-G factor computed by ZM in system $S_1$ is as good as that computed in $M_1$,
  and is presented in SI.}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
\caption{ The splitting parameter dependency in calculating the Kirkwood-G
factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
\color{blue} This is also not shown in your report. right? } \recheck{Right, it was not shown.}]}
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. In Fig.~\ref%
{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
Kirkwood-G factor than smaller splitting parameters.
Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
SI). Note that in many cases the discrepancies from the SPME were relatively
prominent in the middle range of the distance and they tend small for larger
distance.

@@

Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
RF method converges at 6~ps, while the ZM method converges only in 2~ps,
which is consistent with the SPME result. The value of ZM $l=1$ method is
different from the rest ZM methods and SPME result, but the results was
improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about \recheck{ $1.9\%$ for $l=1$ and 0.3\% for $l=2$,}
% {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order ZM method
present lower amplitude oscillation, and when $l\geq 3$, the improvement is
dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. } \recheck{I agree, if the
reason is not clear for us, we should not touch this topic.}]

@@

{\color{red} At cut-off radius of 1.2~nm, the recommended choices of
parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
accuracy in computing the excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal expansion
coefficient, dielectric constant diffusion constant and viscosity. The order 
$l=2$ performs better in reproducing the pressure than $l=3$ (10
v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
negligible). Both of orders 2 and 3 are not sensitive to the splitting
parameter up to 1.0~$\text{nm}^{-1}$.} {\color{blue} Although further
increasing the splitting parameter will push the accuracy of RDF in case $l=2
$ to as high as $l=3$, the pressure accuracy decreases (anti-damping
effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
should be noticed that the recommended parameters indicate $5$\% error
(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
factor for the smallest $S_{1}$? \ If so, how was the results? \recheck{see the added
  in Sec. IV B and SI}] If we seek
more accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. } 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.

>>>>

%2multibyte Version: 5.50.0.2952 CodePage: 932
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
% \input{tcilatex}
% \input{tcilatex}

@@

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2952}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Thursday, November 13, 2014 17:19:51}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

@@

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\date{\today}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses group cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
} [{\color{red} please see the red part in Sec. III B. The order of the
paragraphs are also rearranged.}][ {\color{blue} I added comments.}]

@@

All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs,
pronk2013gromacs} complied by GNU C compiler with single-precision floating
point. The size of the systems and corresponding number of molecules used
for MD simulations are summarized in Tab.~\ref{tab:tmp1}. The benchmark
quantities were calculated in either canonical (NVT) or isothermal-isobaric
(NPT) ensemble, with equilibrium temperature $T=300$~K. In order to simulate
at the desired temperature, the systems $S_{1}$ and $S_{1}^{\prime }$ were
coupled to Nos\'{e}-Hoover~\cite{nose1984molecular,hoover1985canonical}
thermostat with time-scale $\tau _{T}=1.0$~ps, while systems $M_{1}$, $%
M_{1}^{\prime }$, $L_{0}$, $L_{1}$ and $L_{1}^{\prime }$ were coupled to
Langevin thermostat with time-scale $\tau _{T}=0.1$~ps. In the NPT
simulations, the systems were further coupled to the Parrinello-Rahman
barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs
implementation) with time-scale $\tau _{P}=0.5$~ps to equilibrate the system
at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
of $0.001$~ps.

The neighbor lists were updated every 5 time-steps. {\color{red} The Gromacs
by default uses the group cut-off scheme, while the ZM method suggests an
atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}.} [{%
\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
correct. Or, here, you want to say the "neighbor list making" is done by
group cut-off? (I reread your "cutoff.pdf")} \recheck{the default is rcoulomb = rlist. both
the neighbor list making and the force computing are in group manner.
I prefer not describing this issue in the paper in detail, because the reader
may not be familiar with the terminology (rlist, rcoulomb, and so on) and
the mechanism behind. I think describing how to use ZM correctly in gromacs is enough.
}] The difference between these
cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
based cut-off scheme in the simulations using the SPME (short-range part)
and ZM electrostatic methods. In order to mimic the atom cut-off scheme in
the Gromacs group cut-off implementation, the radius for neighbor list
updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off).

@@

The short-range part of SPME method was cut-offed at $1.9$~nm, and was
smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
These parameters were chosen to be more accurate than the Gromacs default
choices (grid spacing $0.12$~nm and interpolation order $4$).
The conducting boundary condition was used with SPME.
The splitting parameter was optimized by the error estimate, which is
implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
reciprocal space force computing errors were equally distributed as $%
1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
the limit of the single-precision representation of the floating point
numbers. % [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]

@@

In the simulations using RF method, the electrostatic interactions were cut-off in the
group manner (Gromacs default), so the radius for neighbor list updating is set identical to
the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
  for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
\recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
\varepsilon _{\text{rf}}=80$.

The van der Waals interaction was always cut-offed at $1.2$~nm, and it was
modified in a shell of $0.05$~nm width near the cut-off sphere by the
Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
The final configuration of $L_{1}^{\prime }$ was used as initial
configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
which means the system is in desired thermodynamic state.

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is little. Although the splitting parameter, $\alpha $,
also does not have significant influence on almost all these thermodynamic
quantities for $l=1$, only the isothermal compressibility admits a weak
dependence. Overall, the ZM\ agrees with the SPME results without any bias
and out-performs the RF.

It should be noticed that in the calculation of the chemical
potential, the energy correction plays an important role. In the case of $%
l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
final result. By increasing $l$ or $\alpha $, this contribution becomes more
significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
respectively. [{\color{blue}COMMENT: We will clarify what is the "energy
correction" after making SecII, and describe the relation to IPSp after
making Appendix B.}]

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
\caption{The pressure convergence with respect to the cut-off radius. The ZM
methods with order from 1 to 4 are compared with the RF. The splitting
parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
The black solid line indicates the magnitude of the correct pressure: 1~Bar.
The error bars present the statistical uncertainty at 95\% confidence level. 
{\color{red} This uncertainty is twice of the standard deviation of the
estimates (which are averages along MD trajectories) that is calculated by
the block average method~\protect\cite{janke2002statistical}.} [ {\ 
\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
\color{blue} another COMMENT: In these figures, can we see the statistical
uncertainty of the pressure obtained by the SPME? Viz., I found no error
bars for SPME.} \recheck{NO SPME result is given in this figure!}]}
\label{fig:pres-comp}
\end{figure}

@@

It should be noted that even with the system $L_{0}$ that contains 13824
water molecules, the fluctuation (measured by standard deviation) of the
pressure is roughly 100~Bar, which means that it is very difficult to
achieve very accurate estimate for this quantity.
\recheck{In practice a pressure
error of 20~Bar will only cause a
density deviation (calculated by the NPT simulations) of roughly 0.1\%.
Taking different orders ZM method at cut-off 1.2~nm for example,
the density deviations are 0.051\%, 0.061\%, 0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively.
For $l\leq 3$ the pressure error is less than 20~Bar, while for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
}

[{\color{blue} COMMENT1: Can we have a
trajectory figure of the pressure? It will show that the fluctuation is
large and the 10 Bar error for ZM looks small. If there is a suitable one,
it may be good to put it in SI.} \recheck{Could you explain why? The SD should be enough for our purpose.}] [ {\color{blue} COMMENT2: Can we have some
data on the (mass) density? Some potential users of ZM\ may worry about the
deviation of the density from the reality due to the pressure error. I
remember that the density error for ZM was small. It is helpful to show that
the deviation of the density is sufficiently small. These two comments
indicates that one wants to feel how good or bad about the 10 Bar error.} \recheck{Done}]

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any system-size dependency and indicate $r_{\text{%
c}}\sim 1.2\,$nm\ being suffice for the accuracy. Since a slow convergence
is also known for the dielectric constant, we have monitored the behavior as
shown in Fig.~\ref{fig:eps-conv}, and confirm the sufficient convergence
w.r.t.~the length of the trajectories.

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
method is qualitatively wrong, and the accuracy of the ZM method is much
higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
highly consistent with the SPME result, and $l=2$ seems the best. In the
system of larger size ($L_{1}$), the accuracies of the ZM method is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. 
The Kirkwood-G factor computed by ZM in system $S_{1}$ is as
good as that computed in $M_{1}$, and is presented in SI.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
\caption{ The splitting parameter dependency in calculating the Kirkwood-G
factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
uncertainty is presented at 95~\% confidence level by the error bars. }
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1},
it shows that in the case of $l=1$, the largest splitting parameter ($\alpha
=2.0\ \text{nm}^{-1}$) is worse in calculating the Kirkwood-G factor than
smaller splitting parameters. Splitting parameter dependency was not so
clear for $l=2$ and 3 (shown in SI). Note that in many cases the
discrepancies from the SPME were relatively prominent in the middle range of
the distance and they tend small for larger distance.

@@

Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
RF method converges at 6~ps, while the ZM method converges only in 2~ps,
which is consistent with the SPME result. The value of ZM $l=1$ method is
different from the rest ZM methods and SPME result, but the results was
improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}. 
Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the
convergence is quick for a large $\alpha $.

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$)
with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $1.9\%$
for $l=1$ and ${0.3\%}$ for $l=2$, % {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order
ZM method present lower amplitude oscillation, and when $l\geq 3$, the
improvement is dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. } {\color{red} I
agree, if the reason is not clear for us, we should not touch this topic.}][ 
{\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
to reconsider this issue, it may be useful to calculate the RDF with H-H
length (MD trajectory also remains). Deviations should be larger for H-H
than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
and the H-H length is just the twice of this 0.6 nm). Rather, the true
reason may be other, e.g., group cuotff MD scheme may intrinsically give the
accracy at least for RDF. }]

@@

At cut-off radius of 1.2~nm, the recommended choices of
parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
accuracy in computing the excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal expansion
coefficient, dielectric constant diffusion constant and viscosity. The order 
$l=2$ performs better in reproducing the pressure than $l=3$ (10
v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
negligible). Both of orders 2 and 3 are not sensitive to the splitting
parameter up to 1.0~$\text{nm}^{-1}$. Although further
increasing the splitting parameter will push the accuracy of RDF in case $%
l=2 $ to as high as $l=3$, the pressure accuracy decreases (anti-damping
effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
should be noticed that the recommended parameters indicate $5$\% error
(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
containing 13,824 molecules).  If we seek more
accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.
